---
title: "Visualize Data"
output: html_notebook
---

### Your Turn 5: The ggplot template and aesthetics

Run the following code chunk to import the COVID19 data.

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lubridate)

covid_testing <- read_csv("covid_testing.csv") 
```



Let's recreate the histogram of *pan_day*. 

You will need to:

1. Pick a data set: *covid_testing*
2. Choose a geom function: *geom_histogram()*
3. Map aesthetic properties of the graph to variables of the data frame (in this case, the *pan_day* variable should be on the x axis).

Fill in the blanks and run the code to create the plot.

(Hint: if you get stuck, take a look at the slide titled "ggplot()"!)

```{r}
ggplot(data = ______) +
  ______(mapping = aes(x = ______))
```




When you run this code, you will most likely have what looks like an error displayed above the graph:

  `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.

This is actually just a message from R, telling you that it's a bad idea to use a default bin width. 

The *pan_day* variable holds the day of the pandemic (an arbitrary day in late February of 2020) on which the COVID test order was placed. What would be an appropriate binwidth for *pan_day* to see *daily* test volumes?

Now fill in the blanks below to recreate the code from the previous chunk, with the *binwidth* argument passed to the *geom_histogram* function. 

```{r}
ggplot(______) +
  ______(mapping = aes(______), binwidth = ______)
```




The effect of reducing the bin width (and increasing the number of bins) is that the data is now presented in much greater detail. 

Let's next add some color!

Copy and paste the previous code chunk and add an aesthetic mapping that maps the *fill* aesthetic to the *result* column. (Hint: all aesthetics must be defined *inside* the aes() function!)













***************************************************************************************
***************************************************************************************
***************************************************************************************
***************************************************************************************
***************************************************************************************
********************************                    ***********************************
********************************     Stop here.     ***********************************
********************************                    ***********************************
***************************************************************************************
***************************************************************************************
***************************************************************************************
***************************************************************************************
***************************************************************************************






### Your Turn 6: Geom functions

Run the following code chunk:

```{r}
ggplot(data = covid_testing) +
  geom_histogram(mapping = aes(x = pan_day))
```


Now try to figure out how you would modify the code above so it draws a frequency polygon instead of histogram. 

```{r}

```




Modify the previous code chunk so that the frequency polygon's line color is blue. (Hint: color names go in quotes!)

```{r}

```







What do you think the following code will do? Try to predict what you'll see.

Then run it.

```{r}
ggplot(data = covid_testing) +
  geom_histogram(mapping = aes(x = pan_day)) +
  geom_freqpoly(mapping = aes(x = pan_day))
```

