---
title: "Transform Data"
format: html
editor: visual
---

## select( )

```{r}
select(covid_testing, mrn, last_name)   # select columns to keep
```

## filter( )

```{r}
filter(covid_testing, mrn == 5000078)  # filter to specific rows
```

## Pipes: %\>%

```{r}
covid_testing %>% 
	filter(pan_day <= 10) %>% 
	select(clinic_name)
```

## mutate( )

```{r}
covid_testing %>%
	mutate(c_r_tat_mins = col_rec_tat*60)
```

## Your Turn #1

Use select, filter and %\>% in the following chunk to write a sequence of functions that:

a\) Filters to tests from the clinic (\`clinic_name\`) of "picu"

b\) Selects the column with the received-to-verified turnaround time (\`rec_ver_tat\`) as well as the day from start of the pandemic (\`pan_day\`)

```{r}
_________ %>% # name of data frame goes here
  filter(_______) %>% 
  select(________, ________) 
```

Use mutate with %\>% to create a new column named "total_tat" containing the total turnaround time for each test (sum of \`col_rec_tat\` and \`rec_ver_tat\`). Store this output in the covid_testing object and view the data in a new tab by calling the object with the View( ) function.

```{r}
________ <- ________ %>%
	mutate(total_tat = ________)
View(________)
```

**Stop Here**

## Your Turn #2

You are interested in understanding the relative utilization of COVID tests and the range of turnaround times across locations, which are captured with the clinic_name variable. Use group_by and summarize to calculate:

a\) The number of orders ordered by each clinic/unit, creating a new summary variable num_orders

b\) The median total turnaround time for each clinic/unit (using the total_tat variable you created in the previous exercise), using a new summary variable median_tat.

The function to calculate a median is (predictably) median(...).

Store the output from your summarization in a new object called covid_summary.

```{r}
covid_summary <- ________ %>%
  group_by(________) %>%
  summarize(num_orders = ________,
            median_tat = ________)
View(covid_summary)
```
