---
title: "Transform Data"
---

## select()

```{r select}
select(covid_testing, mrn, last_name)   # select columns to keep
```


## filter()

```{r}
filter(covid_testing, mrn == 5000078)  # filter to specific rows
```

## %>%

```{r}
covid_testing %>% 
	filter(pan_day <= 10) %>% 
	select(clinic_name)
```


## mutate()

```{r}
covid_testing %>%
	mutate(c_r_tat_mins = col_rec_tat*60)
```


## Your Turn 1

Use select, filter and %>% in the following chunk to write a sequence of functions that: 

1. Filters to tests from the clinic (`clinic_name`) of "picu"

2. Selects the column with the received-to-verified turnaround time (`rec_ver_tat`) as well as the day from start of the pandemic (`pan_day`)

```{r Your Turn}
covid_testing %>% # name of data goes here
  filter(clinic_name == "picu") %>% 
  select(pan_day, clinic_name) 
```

Use mutate with %>% to create a new column named "total_tat" containing the total turnaround time for each test (sum of `col_rec_tat` and `rec_ver_tat`).

```{r}
covid_testing %>%
	mutate(total_tat = col_rec_tat + rec_ver_tat)
```
